### 2019-04-26 Sections/conclusion_the_vision_of_the_quantum_internet.tex
Global overview fig+

@@

>>>>

\comment{Include ref} %Fig.~\ref{fig:integrated_services_overview}

@@

\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{integrated_services_overview}
	\captionspacefig \caption{Overview of some of the essential services integrated into a future globally-unified quantum internet ecosystem.}\label{fig:integrated_services_overview}
\end{figure*}

### 2019-04-26 Sections/intro_to_QIT.tex
Global overview fig+

\begin{figure}[hbt]
\includegraphics[clip=true, width=0.4\textwidth]{classical_mutual_info.pdf}
\captionspacefig \caption{\label{fig:mutual_info}}	
\end{figure}

@@

Now, in sharp contrast with the classical case, the conditional entropy for quantum states
\begin{align}
H(A| B) = S(\hat \rho_{AB}) - S(\hat \rho_B)
\label{cond_quant_ent}
\end{align}
\noindent can be negative! If $\rho_{AB}$ is a maximally entangled state, then 
$S(\hat \rho_{AB}) =0$, and $H(A|B) =- S(\hat \rho_{AB}) <0$.
Intuitively, this can be interpreted as the fact that bipartite maximally entangled states can be more strongly correlated than classically possible, and that knowing the state of $A$ reveals an ``unnatural" amount of information about the state of $B$.

@@

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum channel we have the flexibility to manipulate the input state and the measurement at the output. From this, we can then define the \textit{classical information of the channel}\index{Classical information of the channel}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from which they would like to extract maximal correlations (i.e joint information). They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. Their quantum mutual information of the channel is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\rho,\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B). 
\label{eq:quant_mut}
\end{align}

Eq.~\eqref{eq:quant_mut} quantifies the maximum amount of correlation that can be established between input and output states that can be achieved across the channel. This dictates the physical upper bound on the achievable bitrate (classical communication) or bandwidth of the channel.

% \paragraph{Quantum correlation measures}

We now move on to discuss quantum correlations. Whilst classical correlation measures have a clear operational meaning, quantum channel capacities are less so -- these quantities can be interpreted as how well the channel preserves the quantum state.

Analogous to the mutual information for classical systems is the \textit{coherent information} for quantum systems \cite{bib:PhysRevA.54.2629}, defined as,
\begin{align}\index{Coherent information}
I_\text{coh}(\hat\rho,\mathcal{E}) = S(\mathcal{E}(\hat\rho)) - S_e(\hat\rho,\mathcal{E}).
\label{eq:mutual_info_classical_single}
\end{align}
Here $S_e$ is the \textit{exchange entropy}, a measure of how much information is exchanged between the state $\hat\rho$ and the environment under the action of the process. Specifically, it is given by the entropy of the environment subsystem in Eq.~(\ref{eq:proc_environment}), after application of the channel. This yields the intuitive interpretation that the coherent information is the information contained in the evolved state, discounted by the amount lost to the environment. It can be alternatively written as,
\begin{align}
I(A\rangle B) = H(B)_{\hat\rho} - H(A,B)_{\hat\rho},
\end{align}
which we recognise as the negative of the conditional quantum entropy in Eq~\eqref{cond_quant_ent}.

The fact that the information quantity $H(A|B)$ can be negative is a signature of the fundamental difference between the laws of classical and quantum information.

>>>>

\begin{figure}[!hbtp]
%\includegraphics[clip=true, width=0.4\textwidth]{classical_mutual_info.pdf}
\captionspacefig \caption{\label{fig:mutual_info}}	
\end{figure}

@@

Now, in sharp contrast with the classical case, the conditional entropy for quantum states
\begin{align}
H(A| B)_{\hat \rho} = S(\hat \rho_{AB}) - S(\hat \rho_B)
\label{cond_quant_ent}
\end{align}
\noindent can be negative! If $\rho_{AB}$ is a maximally entangled state, then 
$S(\hat \rho_{AB}) =0$, and $H(A|B) =- S(\hat \rho_{AB}) <0$.
Intuitively, this can be interpreted as the fact that bipartite maximally entangled states can be more strongly correlated than classically possible, and that knowing the state of $A$ reveals an ``unnatural" amount of information about the state of $B$.

@@

The mutual information is defined as being between a particular known pair of states. Of course, in a quantum channel we have the flexibility to manipulate the input state and the measurement at the output. From this, we can then define the \textit{classical information of the channel}\index{Classical information of the channel}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from which they would like to extract maximal correlations (i.e joint information). They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. The quantum mutual information of the channel $\mathcal{E}$ is defined as,
\begin{align}
I_c(\mathcal{E}) = \max_{\rho,\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B)_\rho. 
\label{eq:channel_quant_mutual}
\end{align}

Eq.~\eqref{eq:channel_quant_mutual} quantifies the maximum amount of correlation that can be established between input and output states that can be achieved across the channel. This dictates the physical upper bound on the achievable bitrate (classical communication) or bandwidth of the channel.

\vspace{5mm}
% \paragraph{Quantum correlation measures}
All of the correlations discussed above concern classical information.
We now move on to discuss quantum correlations. Whilst classical correlation measures have a clear operational meaning, quantum channel capacities are less so -- these quantities can be interpreted as how well the channel preserves the quantum state.

The conditional entropy for quantum states can be negative is significant, in fact, it has its own name and notation, the \textit{coherent information}
\begin{align}
I(A\rangle B) = H(B)_{\hat\rho} - H(A,B)_{\hat\rho},
\end{align}

\noindent For a maximally entangled state, the coherent information is equal to one. It measures to what extent we know less about a subsystem compared to the whole.
